Demystifying the Computer Science \\Ph.D. Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-06-12 phd-cs-us.tex
Updates from Overleaf

In short, if you can come to the Open House, do come.  But if you're international student outside of the US, then likely you cannot come.  So see if you can attend it virtually and ask to meet with individual faculty if you can.

@@

You can learn about CS programs and research expertise of faculty using resources such as \href{https://csrankings.org}{CSRankings.org}, which is designed specifically to help prospective PhD students in Computer Science!  You will be very surprised to learn that a school X that you don't know much about has very strong research in your interested field Y. This is also a good way to learn about individual faculty (who works on what) and the well-known CS conferences\footnote{In CS (and only in CS), conferences, not journals, are oten the main venue to publish research finding.}.
\begin{commentbox}
    Dat: many Vietnamese students, including those from very top engineering schools, do not know about CSRankings.  May be applicants who worked at top research places such as VinAI might know about it.
\end{commentbox}

@@

\subsection{Current 2023 Rankings of CS PhD programs in the U.S}\label{sec:ranking}
  Tab.~\ref{tab:ranking} lists the top 50 CS programs in the US from \href{https://www.csrankings.org}{CSRankings.org}, a ranking system  based on top CS conferences.

  \begin{table}[h!]
    \centering
    \small
    \caption{Top 50 CS PhD programs in the U.S. (CSRankings, June 2023)}\label{tab:ranking}
  \begin{tabular}{rl|rl}
    \toprule
    1 & Carnegie Mellon & 26 & Univ. of California - Irvine \\
    2 & Univ. of Illinois at Urbana-Champaign  & 27 &  Duke University \\
    3 & Univ. of California-San Diego & 28 & Rutgers University \\
    4 & MIT & 29 & Univ. of California - Riverside\\
    5 & Georgia Institute of Technology         & 30 & Northwestern University\\
    6 & Stanford University& 31 & Pennsylvania State University  \\
    7 & University of Michigan - Ann Arbor   & 32& George Mason University\\  
    8 & University of Washington      &33 &  Harvard University \\
    9 &  Univ. of California - Berkeley  &34&  Univ. of California - Santa Cruz \\
    10 & Cornell University  & 35 &  Yale University \\
    11 & University of Maryland - College Park &  36& Brown University \\ 
    12 & Northeastern University &37&  Ohio State University\\
    13 & University of Wisconsin - Madison  &38& Texas A\&M University \\
    14 & Columbia University   &39 & Boston University  \\
    15 &   Purdue University  &40& North Carolina State University\\\  
    16 & University of Texas at Austin   &41 & University of Utah \\
    17 & University of Pennsylvania &42 & University at Buffalo\\
    18 & Princeton University  & 43& Rice University\\
    19 & University of Massachusetts-Amherst & 44&  University of Colorado-Boulder \\
    20 &  New York University  &45& University of Illinois at Chicago  \\
    21 & Univ. of California - Los Angeles &46& Virginia Tech  \\
    22 & University of Southern California &47&  Arizona State University \\
    23 & Stony Brook University &48&University of Minnesota \\
    24 & University of Chicago &49& University of Virginia \\
    25 & Univ. of California - Santa Barbara &50& University of North Carolina \\
    \bottomrule
    \end{tabular}
\end{table}

>>>>

In short, if you can come to the Open House, do come.  But if you're international student outside of the US, then likely you cannot come.  So see if you can attend it virtually and meet with individual faculty.

@@

You can learn about CS programs and research expertise of faculty using resources such as \href{https://csrankings.org}{CSRankings.org}, which is designed specifically to help prospective PhD students in Computer Science!  You will be very surprised to learn that a school X that you don't know much about has very strong research in your interested field Y. This is also a good way to learn about individual faculty (who works on what) and the well-known CS conferences\footnote{In CS (and only in CS), conferences, not journals, are often the main venue to publish research finding.}. \S\ref{sec:ranking} gives the top 50 CS programs in the US according to CSRankings.
\begin{commentbox}
    Dat: many Vietnamese students, including those from top engineering schools, do not know about CSRankings.  May be applicants who worked at top research places such as VinAI would know about it.
\end{commentbox}

@@

\section{Rankings of CS PhD programs in the U.S}\label{sec:ranking}
  Tab.~\ref{tab:ranking} lists the top 50 CS programs in the US from \href{https://www.csrankings.org}{CSRankings.org}, a ranking system  based on top CS conferences.

  \begin{table}[h!]
    \centering
    \small
    \caption{Top 50 CS PhD programs in the U.S. (CSRankings, June 2023).  $^*$ indicates the university has a \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Viet-CS-Profs-US}{Vietnamese prof.} that can advise CS Ph.D. students.}\label{tab:ranking}
  \begin{tabular}{rl|rl}
    \toprule
    1 & Carnegie Mellon & 26 & Univ. of California - Irvine \\
    2 & Univ. of Illinois at Urbana-Champaign$^*$  & 27 &  Duke University \\
    3 & Univ. of California-San Diego & 28 & Rutgers University$^*$ \\
    4 & MIT & 29 & Univ. of California - Riverside\\
    5 & Georgia Institute of Technology         & 30 & Northwestern University\\
    6 & Stanford University& 31 & Pennsylvania State University  \\
    7 & University of Michigan - Ann Arbor   & 32& George Mason University$^*$\\  
    8 & University of Washington      &33 &  Harvard University \\
    9 &  Univ. of California - Berkeley  &34&  Univ. of California - Santa Cruz \\
    10 & Cornell University  & 35 &  Yale University \\
    11 & University of Maryland - College Park &  36& Brown University \\ 
    12 & Northeastern University$^*$ &37&  Ohio State University\\
    13 & University of Wisconsin - Madison$^*$  &38& Texas A\&M University$^*$ \\
    14 & Columbia University   &39 & Boston University  \\
    15 &   Purdue University  &40& North Carolina State University\\\  
    16 & University of Texas at Austin   &41 & University of Utah \\
    17 & University of Pennsylvania$^*$ &42 & University at Buffalo\\
    18 & Princeton University  & 43& Rice University\\
    19 & University of Massachusetts-Amherst$^*$ & 44&  University of Colorado-Boulder \\
    20 &  New York University  &45& University of Illinois at Chicago  \\
    21 & Univ. of California - Los Angeles &46& Virginia Tech$^*$  \\
    22 & University of Southern California &47&  Arizona State University$^*$ \\
    23 & Stony Brook University$^*$ &48&University of Minnesota \\
    24 & University of Chicago &49& University of Virginia \\
    25 & Univ. of California - Santa Barbara &50& University of North Carolina$^*$ \\
    \bottomrule
    \end{tabular}
\end{table}
